\LARGE \bf Geometric Adaptive Control of Attitude Dynamics on $\SO$\\ with State Inequality Constraints

### 2015-09-24 ACC16.2.tex
finished sim and started experimental section. changed pdf names. run epstopdf rather than letting latex do it.

\section{Numerical Examples}
We demonstrate the performance of the proposed control system via numerical simulation.
The inertia tensor of a rigid body is given as
\begin{gather*}
	J = \begin{bmatrix}
	\num{5.571e-3} & \num{6.177e-5} & \num{-2.503e-5} \\
	\num{6.177e-5} & \num{5.571e-3} & \num{1.001e-5} \\
	\num{-2.503e-5} & \num{1.007e-5} & \num{1.051e-2}
	\end{bmatrix} \, .
\end{gather*} 
The control system parameters are chosen as
\begin{gather*}
	G = \text{diag} \parenth{0.9,1.1,1.0}\, , \quad k_R = 0.4 \, , \quad	k_\Omega = 0.296 \, ,\\
	c = 1.0 \, , \quad k_\Delta = 0.5 \, , \quad \alpha = 15 \, .
\end{gather*}
A body fixed sensor is defined as
\begin{gather*}
	r = \begin{bmatrix} 1 & 0 & 0 \end{bmatrix} \, ,
\end{gather*}
while multiple inequality constraints are defined in~\cref{tab:constraints}.
The simulation parameters are chosen to emulate those found in~\cite{lee2011b}.
\begin{table}[htbp]
\begin{center}\begin{tabular}{lc}
Constraint Vector & Angle \\ \hline \hline 
\(\begin{bmatrix} 0.174 &-0.934 & -0.034 \end{bmatrix}\) & \ang{40} \\ \hline 
\(\begin{bmatrix} 0 & 0.7071 & 0.7071 \end{bmatrix}\) & \ang{40} \\ \hline 
\(\begin{bmatrix} -0.853 & 0.436 & -0.286 \end{bmatrix}\) & \ang{40} \\ \hline 
\(\begin{bmatrix} -0.122 -0.140 -0.983 \end{bmatrix}\) & \ang{20}\end{tabular} 
\caption{Simulation Parameters}
\end{center}
\label{tab:constraints}
\end{table}
The initial and desired states are defined using Euler angles as~\cite{shuster1993},
\begin{gather*}
	R(0) = I \, , \quad \Omega(0) = 0 \, ,\\
	R_d = ROT3(\ang{225}) \, , \quad \Omega_d = 0 \, .
\end{gather*}

@@

A hexrotor unmanned aerial vehicle (UAV) has been developed at the Flight Dynamics and Controls Laboratory(FDCL) at the George Washington University.
The UAV is composed of three pairs of counter-rotating propellers. 
Typical quadrotor UAVs are composed of four or more co-planar propellers.
As a result, these systems are underactuated and unable to impart a force along every degree of freedom.
For example, quadrotor UAVs are unable to translate laterally without first conducting a rotation.
Conversely, the propeller pairs of the hexrotor are angled relative to one another to allow for a fully actuated rigid body.
This allows the hexrotor to impart a force in any direction and a moment about any axis. (cite hexrotor paper)

The hexrotor UAV is composed of the following parts:
\begin{itemize}
	\item ODROID processor 
	\item Wifi connectivity
	\item VectorNav IMU
	\item Vicon motion capture sent from command computer
\end{itemize}

Describe aim of experiment. 
Demonstrate that hexrotor fixed sensor can stabilize to desired attitude while avoiding an obstacle.s
Mount a sphere at an appropriate distance such that the subtended angle is equal to the cone constraint

Show plots of response with and without avoidance term
Response should be similar to numerical simulation

\section{Conclusions}

>>>>

\section{Numerical Examples}
We demonstrate the performance of the proposed control system via numerical simulation.
The inertia tensor of a rigid body is given as
\begin{gather*}
	J = \begin{bmatrix}
	\num{5.571e-3} & \num{6.177e-5} & \num{-2.503e-5} \\
	\num{6.177e-5} & \num{5.571e-3} & \num{1.001e-5} \\
	\num{-2.503e-5} & \num{1.007e-5} & \num{1.051e-2}
	\end{bmatrix} \, .
\end{gather*} 
The control system parameters are chosen as
\begin{gather*}
	G = \text{diag} \parenth{0.9,1.1,1.0}\, , \quad k_R = 0.4 \, , \quad	k_\Omega = 0.296 \, ,\\
	c = 1.0 \, , \quad k_\Delta = 0.5 \, , \quad \alpha = 15 \, .
\end{gather*}
A body fixed sensor is defined as
\begin{gather*}
	r = \begin{bmatrix} 1 & 0 & 0 \end{bmatrix} \, ,
\end{gather*}
while multiple inequality constraints are defined in~\cref{tab:constraints}.
The simulation parameters are chosen to emulate those found in~\cite{lee2011b}.
\begin{table}[htbp]
\begin{center}\begin{tabular}{lc}
Constraint Vector & Angle \\ \hline \hline 
\(\begin{bmatrix} 0.174 &-0.934 & -0.034 \end{bmatrix}\) & \ang{40} \\ \hline 
\(\begin{bmatrix} 0 & 0.7071 & 0.7071 \end{bmatrix}\) & \ang{40} \\ \hline 
\(\begin{bmatrix} -0.853 & 0.436 & -0.286 \end{bmatrix}\) & \ang{40} \\ \hline 
\(\begin{bmatrix} -0.122 -0.140 -0.983 \end{bmatrix}\) & \ang{20}\end{tabular} 
\caption{Simulation Parameters}
\end{center}
\label{tab:constraints}
\end{table}
The initial and desired states are defined using Euler angles as~\cite{shuster1993},
\begin{gather*}
	R(0) = I \, , \quad \Omega(0) = 0 \, ,\\
	R_d = \text{ROT3}(\ang{225}) \, , \quad \Omega_d = 0 \, .
\end{gather*}

@@

A hexrotor unmanned aerial vehicle (UAV) has been developed at the Flight Dynamics and Controls Laboratory(FDCL) at the George Washington University.
The UAV is composed of three pairs of counter-rotating propellers. 
Typical quadrotor UAVs are composed of four or more co-planar propellers.
As a result, these systems are underactuated and unable to impart a force along every degree of freedom.
For example, quadrotor UAVs are unable to translate laterally without first conducting a rotation.
Conversely, the propeller pairs of the hexrotor are angled relative to one another to allow for a fully actuated rigid body.
This allows the hexrotor to impart a force in any direction and a moment about any axis.

The hexrotor UAV is composed of the following hardware:
\begin{itemize}
	\item ODROID processor 
	\item Wifi connectivity blurb
	\item VectorNav IMU 
	\item Brushless DC Motors 
	\item Vicon motion capture sent from command computer
\end{itemize}
In order to constrain the motion and test only the attitude dynamics we attach the hexrotor to a spherical joint.
The center of rotation is below the center of gravity of the hexrotor.
As a result, there is a destabilizing gravitational moment and the resulting attitude dynamics is similar to an inverted pendulum model.
We augment the control input in~\cref{eqn:adaptive_control} with an additional term to negate the effect of the gravitational moment.

A sensor is defined in the body frame of the hexrotor as \( r = \begin{bmatrix} 1 & 0 & 0 \end{bmatrix}^T \).
We define an obstacle in the inertial frame as \( v = \begin{bmatrix} \frac{1}{\sqrt{2}} & \frac{1}{\sqrt{2}} & 0\end{bmatrix}^T \) with \( \theta = \ang{10} \).
An inertial and desired attitude are defined in terms of Euler angles as
\begin{gather}
	R(0) = \text{ROT3}(\ang{90}) \, , \quad R_d = \text{ROT3}(\ang{0}) \, ,
\end{gather}                                
this results in the sensor performing a \ang{90} yaw rotation about the vertical axis of the spherical joint.

Picture of test set up
Plots of response and trajectory
Link to video

The experimental results are shown in FIGURE.
It shows acceptable attitude stabilization performance.
The attitude errors asymptotically converge to zero. 
In addition, as the constraint is neared an out-of-plane moment is used to avoid the constrained region.
The control system is computed autonomously on-board the UAV.
This is in constrast to many state constrained attitude control systems which require an a priori attitude trajectory to be calculated. 
\section{Conclusions}
